\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-04-22 paper.tex
'Small' corrections from reviewer 1
Includes anyway a few rewrite of sections

\usepackage[nomargin, marginclue, footnote]{fixme}

@@

From an artificial intelligence perspective, {\sc Spark} takes care of merging
sensing modalities, it computes and grounds perceptions into symbolic
knowledge (situation assessment), it is responsible temporal interpretation of
situations and performs spatial perspective-taking.

@@

   \caption{ The scenario involves a several videotapes that have to be
       manipulated. Other objects are used as supports and containers.  After
       identification and localisation of the set of objects and acquisition of
       the position and posture of the human partner, the robot is able to compute
       that two tapes only are reachable by itself: the \concept{LOTR\_TAPE}
       (black in the 3D model) and \concept{GREY\_TAPE}. The third tape
       \concept{WALLE\_TAPE} (white in the 3D model) and the trashbin
       \concept{PINK\_TRASHBIN} are only reachable by the human. The
       corresponding symbolic facts are listed in Table~\ref{table|beliefsfig7}.
   }%

@@

Geometric state of the world is abstracted in symbolic facts that can
be classified in three different categories.

\begin {itemize}
\item Relative positions of object and agents, e.g.  \stmt{GREY\_TAPE
    isOn TABLE}.

\item Perception and manipulation capacity and state of agents,
  e.g. \stmt{ROBOT looksAt GREY\_TAPE}, \stmt{GREY\_TAPE isVisibleBy
    HUMAN1}.

\item Motion status for object or agent parts, e.g.  \stmt{GREY\_TAPE
    isMoving true},\\ \stmt{ROBOT\_HEAD isTurning true}.
\end {itemize}

Reasoning about human perspective allow to compute facts such as:
\stmt{GREY\_TAPE isBehind HUMAN1}, \stmt{GREY\_TAPE leftOf
  HUMAN1}.

Figure~\ref{fig::reach-ex} illustrates different situations for the
\textit{reachable} relation.

\begin{figure*}[!t]
	\centering
    \subfigure[] { \includegraphics[width=0.2\textwidth]{reachex-1.png} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-2.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-3.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-4.jpg} }
    \caption{An example illustrating the \textit{reachable} relation. The
        relation is computed from the perspectives of both the robot and the
        human. The computed posture at each step is illustrated with a global
        view of the scene (top), and from a closest view (bottom). The robot
        and its human partner are placed face to face (a).  The robot first
        estimates if the small grey box is reachable to itself. This is done by
        finding a collision free posture to reach the object (b). Next the
        robot switches to the human's perspective to estimate if the same
        object is reachable to the human as well (c).  In the last scene, the
        human moves towards his left, farther from the object (d). The
        situation is then reevaluated. In this occasion though, the reasoner
        cannot find a satisfactory posture for the human to reach the box
        because he is too far from the target.  }

@@

\paragraph{Hypotheses on objects states and positions}
It is sometimes difficult or even impossible to see and/or track an
object in certain states. This happens, for instance, when the object
is hidden in a container, when the robot holds it in its gripper, and more
generally in any state in which it is hidden by something else. {\sc Spark} models the possible symbolic states of objects (whether the object is on a furniture, in an agent hand,
in a container, etc.): According to the robot perception of what has
happened since the object was last seen, the robot builds a
belief of the current possible state with associated probability for the.

\paragraph{Primitive action recognition} Monitoring human activity is crucial
to maintain a coherent state of the world. Full human action and activity
monitoring is a task that requires knowledge and reasoning both on high level
facts like goals, intentions and plans, as well as bottom-up data from agent
and object motions. Simple temporal and geometric reasoning on human hand
trajectories and potential objects placements can provide some useful clues for
high level human monitoring processes. We call this temporal and geometric
reasoning \emph{primitive action recognition}. Those primitive actions are
assessed through monitoring situations like ``an empty hand is close to an
object on a table'' (precursor for a \emph{pick}), or ``a hand holding an
object is over a container'' (precursor for a \emph{throw}).

@@

First, particular steps of the grounding process explicitly check for the
presence and value of specific facts: for instance, when several instances
matches a category (the human says ``give me the bottle'' and the robot knows
about three bottles), the module may decide (it actually depends on the
quantifier preceding the class) to discard some of them based on their
\emph{visibility} for the speaker (implicit communication context built on the
human posture).

@@

The second level of integration of multi-modality is implicit: by computing
symbolic properties from the geometry, richer descriptions and hence
discrimination possibilities are available: for instance, if reachability is
available, the robot may ask ``do you mean the bottle that is accessible to
me?'' to discriminate between the three bottles. That way, procedures relying
on discrimination transparently benefit from added modalities.

@@

\subsection{Human-aware task planning}

@@

HATP originality resides in its ability to produce plans for the robot's
actions \emph{as well as for the other participants} (humans or robots): the
robot plans for itself, but also for its interactors, which effectively endows the robot
with new interaction capabilities: It can partially predict the behavior, and
thus monitor the engagement, of its human partner; the planner generates
synchronisation points (arrow going from the robot stream to the human stream on
Figure~\ref{plan_hatp1}) between the agents; the controller can also verbalize
the plans to explain its partner how a task may be shared~\cite{warnier2012when}.

HATP can be tuned by setting up different costs depending on the actions to
apply and by taking into account a set of constraints called \emph{social
rules}. This tuning aims at adapting the robot's behavior according to the
desired level of cooperation of the robot.

\paragraph{Agents and action streams}
The robot plans not only for itself but also for the other agents. The
resulting plan, called ``shared plan'' is a set of actions that form
a stream for each agent involved in the goal achievement. Depending on
the context, some ``shared plans'' contain causal relations between
agents. For example, the second agent needs to wait for the success of
the first agent's action to be able to start its own action. When the
plan is performed, causal links induce synchronization between
agents. Figure~\ref{plan_hatp1} illustrates a plan with two streams.

@@

\paragraph{Action costs and social rules}
A cost and a duration function is associated to each action.
The duration function provides a duration interval for the action
achievement and is used, in one hand, to schedule the different
streams and, in the other hand, as an additional cost function.
In addition to these costs, HATP also takes into account a set of social
rules.  Social rules are constraints aiming at leading the plan
construction towards the best plan according to some human
preferences. The social rules we have defined so far deal with:

@@

Two important remarks: because HATP is a generic symbolic task planner, we have
been able to design a planning domain at a semantic level which is close to the
one used in the human-robot dialogue (the planner vocabulary contains concepts
like \texttt{give}, \texttt{table}, \texttt{is on}...). Hence only a few
ontology rules have been required to map both the knowledge extracted from the
situation assessment and the statements originated from the verbal interaction
to the planner domain.

Second remark, after some research (see appendix B of~\cite{Lemaignan2012a} for
a detailed discussion)  we have decided to represent neither the planning
domain nor the resulting plans in the knowledge base: the planning domain (with
task pre- and postconditions) is stored in a specific format, outside of the
central declarative knowledge repository, and the plans are directly
communicated to the robot controller. Thus, like many other cognitive
architectures, we have independent declarative and procedural knowledge stores.

@@

@@

Our robot execution controllers (OpenPRS-based {\sc Shary} or Python-based {\sc
pyRobots}) rely on extensive integration with the knowledge base. It serves as the
primary source of information for semantic-aware decision-making.

We split the interaction situations stemming from the situation assessment and
communication components in two categories: \emph{desires} (performative act)
and \emph{experiences} (assertive act).

@@

\emph{Experiences}, on the other hand, comprise of emotions, states and
questions (when asking a question, we consider the human to be in an
\emph{interrogative state}). When the knowledge base states that an agent
\emph{experiences} a particular emotion or state, the execution controller may
decide to handle it, typically by trying to answer the question or using the
emotional or physical state as a parameter for subsequent actions. As an
example, when the speaker says ``I feel tired'', we change the motion planner
parametrization to lower the effort the human needs to provide for the
following joint manipulation tasks. Note that this example has been implemented
as a proof-of-concept. A broader framework that would support action alteration
based on the user's experienced states is yet to be devised.

@@

\begin{tabular}{llll}
 \bf{Experiment} & Focus & \emph{Notes} & Reference \\
\hline
{\it Point \& Learn} (2010) & Interactive knowledge acquisition & & \cite{Lemaignan2010} \\
{\it Spy Game} (2010) & Interactive object discrimination & & \cite{Ros2010b} \\
{\it Moving to London} (2011) & Multi-modal interaction, perspective taking & \emph{immobile robot} & \cite{lemaignan2011what} \\
{\it Roboscopie} (2011) & Theater, reflection on the future of HRI & \emph{semi-autonomous} & \cite{lemaignan2012roboscopie} \\
{\it Cleaning the table} (2011) & Full integration & & \cite{Alami2011} \\
{\it I'm in your shoes} (2012) & False beliefs & & \cite{warnier2012when} \\
{\it Give me this} (2012) & Natural joint object manipulation & & \cite{gharbi2013natural} \\
{\it Aperitif time} (2012) & Multi-modal interaction, perspective taking & & \cite{lemaignan2013talking} \\
\hline

@@

The two following sections present one such experiment (the {\it Moving to
London} scenario), and the synopsis of another one (the {\it Cleaning the
table} scenario).

@@

The second one involves the SHARY execution controller and the HATP symbolic
task planner besides ORO and {\sc Dialogs}. In this scenario, the human and the
robot try to cooperatively remove objects from a table. behaviors and motions
are fully planned.

@@

However both are visible and the cognitive ambiguity resolution cannot be
applied. The only option is to ask Jerry which box he is referring to: ``Which
box, the toolbox or the cardboard box?'' Jerry could answer the
question. Instead, he decides to point at it while indicating: ``This box''
(Figure~\ref{fig|pointing}). The robot's perception identifies the {\tt
cardBoardBox} as being pointed at and looked at by the human and updates the
ontology with this new information using a rule available in the commonsense
ontology ({\tt \textbf{pointsAt}(?ag, ?obj) $\land$ \textbf{looksAt}(?ag, ?obj) $\to$
\textbf{focusesOn}(?ag, ?obj)}) The \textsc{Dialogs} module is then able to merge both
sources of information, verbal (``this'') and deictic to distinguish the box
Jerry refers to.

\begin{center}
\begin{tabular}{l}
\stmt{Jerry pointsAt carboardBox}\\
\stmt{Jerry looksAt carboardBox}\\
$\to$ \stmt{Jerry focusesAt carboardBox}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [cardBoardBox]}
\end{tabular}
\end{center}

Finally, the \textsc{Dialogs} queries the ontology about the content of the box
and the question can be answered: ``Jido-E''. Note that the object's label is
used instead of its ID. This way we enhance interaction using familiar names
given by the users.

\begin{center}
\begin{tabular}{l}
\stmt{?obj isIn cardBoardBox}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = videoTape2}\\
\end{tabular}
\end{center}

@@

This experiment involved a more complex decisional layer where the ORO server
was used in conjunction with the HATP symbolic task planner and the SHARY
execution controller (the complete software architecture we deployed for this
experiment is the one pictured on Figure~\ref{fig|archi},
page~\pageref{fig|archi}).

@@

The plan produced in that case by HATP is straightforward and shown in the
third row. It consists in four successive actions involving the robot and the
human. Robot grasps the tape and then places it on the table at a position
where it is visible and reachable for the human. Human then is asked to pick
the tape and throw it in the trashbin.

@@

\section{Discussion: when AI enables HRI}
\label{sect|conclusion}

@@

The Ke Jia project~\cite{Chen2010} is maybe one of the closest approach. It
integrates on a mobile platform a knowledge representation language with
natural language processing, task planning and motion planning. Default and
non-monotonic reasoning has been especially researched within the Ke Jia
project for symbolic task planing~\cite{Ji2011} and underspecified natural
language processing.

@@

Interaction with humans implies the ability to deal semantics: semantics of
verbal interaction, semantics of gestures, etc.  As a consequence, it also
implies to deal with semantic disambiguation.

>>>>

\usepackage{paralist}

\usepackage[draft, nomargin, marginclue, footnote]{fixme}

@@

From an artificial intelligence perspective, {\sc Spark} takes care of merging
sensing modalities, it computes and grounds perceptions into symbolic
knowledge (situation assessment), it is responsible for temporal interpretation of
situations and performs spatial perspective-taking.

@@

   \caption{The toy scenario pictured here involves videotapes that have to be
       manipulated, with other objects used as supports and containers.  After
       identification and localisation of the set of objects and acquisition of
       the position and posture of the human partner, the robot is able to
       compute that two tapes only are reachable by itself: the
       \concept{LOTR\_TAPE} (black in the 3D model) and \concept{GREY\_TAPE}.
       The third tape \concept{WALLE\_TAPE} (white in the 3D model) and the
   trashbin \concept{PINK\_TRASHBIN} are only reachable by the human. The
   corresponding symbolic facts are listed in Table~\ref{table|beliefsfig7}.  }%

@@

\begin{inparaenum}[\itshape 1\upshape)]
Geometric state of the world is abstracted in symbolic facts that can be
classified in three different categories: \item relative positions of object and
agents, \eg  \stmt{GREY\_TAPE isOn TABLE}, \item perception and manipulation
capacity and state of agents, \eg \stmt{ROBOT looksAt GREY\_TAPE},
\stmt{GREY\_TAPE isVisibleBy HUMAN1}, \item motion status for object or
agent parts, \eg \stmt{GREY\_TAPE isMoving true}, \stmt{ROBOT\_HEAD
isTurning true}.
\end{inparaenum}
By reasoning about human perspective, it computes facts such as:
\stmt{GREY\_TAPE isBehind HUMAN1}, \stmt{GREY\_TAPE leftOf HUMAN1}.

As an illustration, Figure~\ref{fig::reach-ex} explains how the \emph{reachable}
affordance is mutually computed for the human and the robot. The \emph{is visible},
\emph{looks at}, \emph{points at} affordances are computed in similar ways, by
virtually placing OpenGL cameras in different pose (human head pose, robot head
pose, human index finger, etc.) and evaluating which objects are visible to the camera
(hence taking into account possible occlusions).

\begin{figure*}[!t]
	\centering
    \subfigure[] { \includegraphics[width=0.2\textwidth]{reachex-1.png} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-2.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-3.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-4.jpg} }
    \caption{An example illustrating the \textit{reachable} relation. The
        relation is computed from the perspectives of both the robot and the
        human. The computed posture at each step is illustrated with a global
        view of the scene (top), and from a closest view (bottom). The robot
        and its human partner are placed face to face (a).  The robot first
        estimates if the small grey box is reachable to itself using an inverse
        kinematic (IK) solver and collision checks to find a collision free
        posture to reach the object (b). Next the robot switches to the human's
        perspective to estimate if the same object is reachable to the human as
        well (c).  In the last scene, the human moves towards his left, farther
        from the object (d). The situation is then reevaluated. In this occasion
        though, the reasoner cannot find a satisfactory posture for the human to
    reach the box because he is too far from the target.  }

@@

\paragraph{Hypotheses on objects states and positions}

It is sometimes difficult or even impossible to see and/or track an object in
certain states. This happens, for instance, when the object is hidden in a
container, when the robot holds it in its gripper, and more generally in any
state in which it is hidden by something else. {\sc Spark} models the possible
symbolic states of objects (whether the object is on a furniture, in an agent
hand, in a container, etc.): According to the robot perception of what has
happened since the object was last seen, the robot builds a belief of the
current possible state with associated probability model.

\paragraph{Primitive action recognition}

Monitoring human activity is crucial for maintaining a coherent state of the
world. Full human action and activity monitoring is a task that requires
knowledge and reasoning both on high level facts like goals, intentions and
plans, as well as bottom-up data from agent and object motions. Simple temporal
and geometric reasoning on human hand trajectories and potential objects
placements can provide some useful clues for high level human monitoring
processes. We call this temporal and geometric reasoning \emph{primitive action
recognition}. Those primitive actions are assessed through monitoring situations
like ``an empty hand is close to an object on a table'' (precursor for a
\emph{pick}), or ``a hand holding an object is over a container'' (precursor for
a \emph{throw}). \emph{Spark} recognizes a handful \fxfatal{which ones?} of these
primitives, that are relied on by the robot to track the state transitions in
the human plans (as explained below, at section~\ref{hatp}).

@@

First, particular steps of the grounding process explicitly check for the
presence and value of specific facts: for instance, when several instances
match a category (the human says ``give me the bottle'' and the robot knows
about three bottles), the module may decide (it actually depends on the
quantifier preceding the class) to discard some of them based on their
\emph{visibility} for the speaker (implicit communication context built on the
human posture).

@@

The second level of integration of multi-modality is implicit: by computing
symbolic properties from the geometry, richer descriptions and hence
discrimination possibilities are available: for instance, if reachability is
available, the robot may ask ``do you mean the bottle that is accessible to
me?'' to discriminate between the three bottles. That way, procedures relying
on discrimination transparently benefit from added modalities (we kindly refer
the interested readers to~\cite{Ros2010b} for a detailed account of our
approach to interactive concept discrimination with the accompanying algorithms).

@@

\subsection{Human-aware task planning}
\label{hatp}

@@

\paragraph{Agents and action streams}

HATP originality resides in its ability to produce plans for the robot's actions
\emph{as well as for the other participants} (humans or robots), so-called
\emph{shared plans}. This effectively enriches the robot's interaction
capabilities by allowing for a form of \emph{human behaviour prediction}, which
is used in turn by the robot execution controller to monitor the engagement of
the human partner during joint tasks.

The planner also generates synchronisation points between the agents.
Figure~\ref{plan_hatp1} illustrates such a plan with two streams.  Here, the
robot needs to wait for the success of the human agent's {\tt THROW} action
(estimated through the fulfilment of the action post-conditions, typically
$\neg$\stmt{GREY\_TAPE isOn TABLE}) to be able to start its own action.

We also use shared plans to verbalize the sequence of actions and to explain
the human partner how a task may be shared~\cite{warnier2012when}.

@@

\paragraph{Action costs and social rules}

A cost and a duration function is associated to each action.  The duration
function provides a duration interval for the action achievement and is used, in
one hand, to schedule the different streams and, in the other hand, as an
additional cost function.

In addition to these costs, HATP also takes into
account a set of social rules.  Social rules are constraints aiming at leading
the plan construction towards the best plan according to some human preferences.
The social rules we have defined so far deal with:

@@

Because HATP is a generic symbolic task planner, we have been able to design a
planning domain at a semantic level which is close to the one used in the
human-robot dialogue (the planner vocabulary contains concepts like
\texttt{give}, \texttt{table}, \texttt{is on}...). Hence only a few ontology
rules have been required to map both the knowledge extracted from the situation
assessment and the statements originated from the verbal interaction to the
planner domain.

Also, we would like to mention that, after some research (see appendix B
of~\cite{Lemaignan2012a} for a detailed discussion)  we have decided to
represent neither the planning domain nor the resulting plans in the knowledge
base: the planning domain (with task pre- and postconditions) is stored in a
specific format, outside of the central declarative knowledge repository, and
the plans are directly communicated to the robot controller. Thus, like other
cognitive architectures, we have independent declarative and procedural
knowledge stores.

@@

While parts of the architecture (SPARK, ORO) have been deployed with external
execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
on Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the PRS~\cite{Ingrand1996} language. We also use the Python-based
{\sc pyRobots} collection of tools that provide a large set of high-level
actions and an event-based architecture well suited for prototyping.

They both rely on extensive integration with the knowledge base that serves as the
primary source of semantics for decision making.

@@

We split the interaction situations stemming from the situation assessment and
communication components in two categories: \emph{desires} (related to
\emph{performative acts} in Austin's classification of speech
acts~\cite{Austin1962}) and \emph{experiences}.

@@

\emph{Experiences}, on the other hand, comprise of emotions, states and
questions (when asking a question, we consider the human to be in an
\emph{interrogative state}). When the knowledge base states that an agent
\emph{experiences} a particular emotion or state, the execution controller may
decide to handle it, typically by trying to answer the question or using the
emotional or physical state as a parameter for subsequent actions. As an
example, when the speaker says ``I feel tired'', we change the motion planner
parametrization to lower the effort the human needs to provide for the following
joint manipulation tasks.\footnote{Note that this very example has been
implemented as a proof-of-concept. A broader framework that would support
action alteration based on the user's experienced states remains to be worked on.}

@@

\begin{tabular}{llll}
 \bf{Experiment} & Focus & \emph{Notes} & Reference \\
\hline
{\it Point \& Learn} (2010) & Interactive knowledge acquisition & & \cite{Lemaignan2010} \\
{\it Spy Game} (2010) & Interactive object discrimination & & \cite{Ros2010b} \\
{\it Interactive Grounding I} (2011) & Multi-modal interaction, perspective taking & \emph{immobile robot} & \cite{lemaignan2011what} \\
{\it Roboscopie} (2011) & Theater, reflection on the future of HRI & \emph{semi-autonomous} & \cite{lemaignan2012roboscopie} \\
{\it Cleaning the table} (2011) & Whole stack integration & & \cite{Alami2011} \\
{\it I'm in your shoes} (2012) & False beliefs & & \cite{warnier2012when} \\
{\it Give me this} (2012) & Natural joint object manipulation & & \cite{gharbi2013natural} \\
{\it Interactive Grounding II} (2012) & Multi-modal interaction, perspective taking & & \cite{lemaignan2013talking} \\
\hline

@@

The two following sections present one such experiment (the {\it Interactive
Grounding I} scenario), and the synopsis of another one (the {\it Cleaning the
table} scenario).

@@

The second one involves the {\sc Shary} execution controller and the HATP symbolic
task planner besides ORO and {\sc Dialogs}. In this scenario, the human and the
robot try to cooperatively remove objects from a table. behaviors and motions
are fully planned.

@@

However both are visible and the cognitive ambiguity resolution cannot be
applied. The only option is to ask Jerry which box he is referring to: ``Which
box, the toolbox or the cardboard box?'' Jerry could answer the
question. Instead, he decides to point at it while indicating: ``This box''
(Figure~\ref{fig|pointing}). The robot's perception identifies the {\tt
cardBoardBox} as being pointed at and looked at by the human and updates the
ontology with this new information using a rule available in the commonsense
ontology ({\tt \textbf{pointsAt}(?ag, ?obj) $\land$ \textbf{looksAt}(?ag, ?obj) $\to$
\textbf{focusesOn}(?ag, ?obj)}). The \textsc{Dialogs} module is then able to merge both
sources of information, verbal (``this'') and deictic to distinguish the box
Jerry refers to:
\begin{center}
\begin{tabular}{l}
\stmt{Jerry pointsAt carboardBox}\\
\stmt{Jerry looksAt carboardBox}\\
$\to$ \stmt{Jerry focusesAt carboardBox}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [cardBoardBox]}
\end{tabular}
\end{center}

Finally, the \textsc{Dialogs} queries the ontology about the content of the box
and the question can be answered: ``Jido-E''. Note that the object's label is
used instead of its ID. This way we enhance interaction using familiar names
given by the users:

\begin{center}
\stmt{?obj isIn cardBoardBox}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = videoTape2}\\
\end{center}

@@

This experiment involved a more complex decisional layer where the ORO server
was used in conjunction with the HATP symbolic task planner and the {\sc Shary}
execution controller (the complete software architecture we deployed for this
experiment is the one pictured on Figure~\ref{fig|archi},
page~\pageref{fig|archi}).

@@

The plan produced in that case by HATP is straightforward and shown in the
third row. It consists of four successive actions involving the robot and the
human. Robot grasps the tape and then places it on the table at a position
where it is visible and reachable for the human. The human is then asked to pick
the tape and throw it in the trashbin.

@@

\section{Discussion: when Artificial Intelligence enables Human Robot
Interaction}
\label{sect|conclusion}

@@

The Ke Jia project~\cite{Chen2010} is maybe one of the closest approach. It
integrates on a mobile platform a knowledge representation language with
natural language processing, task planning and motion planning. Default and
non-monotonic reasoning has been especially researched within the Ke Jia
project for symbolic task planning~\cite{Ji2011} and underspecified natural
language processing.

@@

Interaction with humans implies the ability to deal with semantics: semantics of
verbal interaction, semantics of gestures, etc.  As a consequence, it also
implies to deal with semantic disambiguation.
